---
output: github_document
bibliography: auryn.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# auryn

auryn will eventually provide an accessible API to the C++ library auryn, which is dedicated to the fast simulation of neural networks with synaptic plasticity [@Zenke2014]. It is currently under development.

## Installation

auryn can be installed from github via

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("sflippl/auryn")
```

## Development

auryn is currently at the beginning of its development. At the moment, it only consists of a reader for files with a .ras extension as the C++ library uses this format to save its output. As an example, you can read in some sample data which has been created using the first example in the [quick start](http://www.fzenke.net/auryn/doku.php?id=quick_start):

```{r}
library(auryn)
read_ras("inst/extdata/poisson.0.ras")
```

The next implemented features will include visualization before going on to more fundamental questions.

# References
